---
output: github_document
---


https://gt.rstudio.com/articles/creating-display-tables.html

>
We can think of display tables as output only, where we’d not want to use them as input ever again. Other features include annotations, table element styling, and text transformations that serve to communicate the subject matter more clearly.

这是gt产生的两个目的

1. 不是需要重复输入的
1. 增加更多解释，方便说明问题

```{r}
library(tidyverse)
```


```{r}
# Take the `islands` dataset and use some
# dplyr functionality to obtain the ten
# biggest islands in the world
islands_tbl <- 
  dplyr::data_frame(
    name = names(islands),
    size = islands
  ) %>%
  dplyr::arrange(desc(size)) %>%
  dplyr::slice(1:10)

# Display the table
library(gt)
gt_tbl <- 
    islands_tbl %>% 
    gt()
```

>
These table parts work well together and there the possible variations in arrangement can handle most tabular presentation needs. 

我觉得这个愿景写的很不错。

add title and subtitle

```{r}
# Make a display table with the `islands_tbl`
# table; put a heading just above the column labels
gt_tbl <- 
  gt_tbl %>%
  tab_header(
    title = "Large Landmasses of the World",
    subtitle = "The top ten largest are presented"
  )

# Show the gt Table
gt_tbl
```

保证了能够像 ggplot 一样展示 table。

用md修饰一下

```{r}
# Use markdown for the heading's `title` and `subtitle` to
# add bold and italicized characters
gt(islands_tbl[1:2,]) %>%
  tab_header(
    title = md("**Large Landmasses of the World**"),
    subtitle = md("The *top two* largest are presented")
  )
```

<input type="checkbox" id="checkbox1" class="styled">什么时候支持`@`写在表格内
[GitHub Issue](https://github.com/rstudio/gt/issues/112)

```{r}
# Display the `islands_tbl` data with a heading and
# two source notes
gt_tbl <- 
  gt_tbl %>%
  tab_source_note(
    source_note = "Source: The World Almanac and Book of Facts, 1975, page 406."
  ) %>%
  tab_source_note(
    source_note = md("Reference: McNeil, D. R. (1977) *Interactive Data Analysis*. Wiley.")
  )

# Show the gt Table
gt_tbl
```

footnote 可以复选单元格

```{r}
# Add footnotes (the same text) to two different
# cell; data cells are targeted with `data_cells()`
gt_tbl <- 
  gt_tbl %>%
  tab_footnote(
    footnote = "The Americas.",
    locations = cells_data(
      columns = vars(name),
      rows = 3:4)
  )

# Show the gt Table
gt_tbl
```

可以使用index T或者F的方式插入‘

```{r}
# Determine the row that contains the
# largest landmass ('Asia')
largest <- 
  islands_tbl %>% 
  arrange(desc(size)) %>%
  slice(1) %>%
  pull(name)

# Create two additional footnotes, using the
# `columns` and `where` arguments of `data_cells()`
gt_tbl <- 
  gt_tbl %>%
  tab_footnote(
    footnote = md("The **largest** by area."),
    locations = cells_data(
      columns = vars(size),
      rows = name == largest)
  ) %>%
  tab_footnote(
    footnote = "The lowest by population.",
    locations = cells_data(
      columns = vars(size),
      rows = name == "Antarctica")
  )

# Show the gt Table
gt_tbl
```


```{r}
# Modify the `airquality` dataset by adding the year
# of the measurements (1973) and limiting to 10 rows
airquality_m <- 
  airquality %>%
  mutate(Year = 1973L) %>%
  slice(1:10)
  
# Create a display table using the `airquality`
# dataset; arrange columns into groups
gt_tbl <- 
  gt(data = airquality_m) %>%
  tab_header(
    title = "New York Air Quality Measurements",
    subtitle = "Daily measurements in New York City (May 1-10, 1973)"
  ) %>%
  tab_spanner(
    label = "Time",
    columns = vars(Year, Month, Day)
  ) %>%
  tab_spanner(
    label = "Measurement",
    columns = vars(Ozone, Solar.R, Wind, Temp)
  )

# Show the gt Table
gt_tbl
```

```{r}
# Move the time-based columns to the start of
# the column series; modify the column labels of
# the measurement-based columns
gt_tbl <- 
  gt_tbl %>%
  cols_move_to_start(
    columns = vars(Year, Month, Day)
  ) %>%
  cols_label(
    Ozone = html("Ozone,<br>ppbV"),
    Solar.R = html("Solar R.,<br>cal/m<sup>2</sup>"),
    Wind = html("Wind,<br>mph"),
    Temp = html("Temp,<br>&deg;F")
  )

# Show the gt Table
gt_tbl
```

<input type="checkbox" id="checkbox1" class="styled">`&deg`正如`&copy`是 html 的展示方式，非latex可以学习一下

这里很好的完成了变量命名的换行功能。